cardinalR: Generating interesting high-dimensional data structures

### 2025-05-04 paper-cardinalR.Rmd
Added S-curve explanantion

>>>>

To simulate an S-curve structure in a higher-dimensional space, we define the function `gen_scurve(n, p)`, which generates `n` observations in `p` dimensions.

The $3\text{-}D$ geometry is constructed by introducing a latent parameter, $\theta \sim U\left(-\frac{3\pi}{2}, \frac{3\pi}{2}\right)$. This parameter controls the curvature of the manifold. The first three dimensions form the S-curve structure:

$$
  X_1 = \sin(\theta), \quad X_2 \sim U(0, 2), \quad X_3 = \text{sign}(\theta) \cdot (\cos(\theta) - 1).
$$

This configuration creates a horizontally curled shape in $(X_1, X_3)$, with additional band thickness in the $X_2$ direction.

For $p > 3$, additional noise dimensions are appended introducing structured, wavy perturbations.
